Nested sampling with two or more objective functions

### 2015-10-08 Paper/ms.tex
Words
Easier-to-understand title

% Full title of the paper (Capitalized)
\Title{Nested sampling with multiple scalars}

@@

Need to be able to sort particles into a total order. So add tiebreaker.

>>>>

% Full title of the paper (Capitalized)
\Title{Nested sampling with two or more objective functions}

@@

Need to be able to sort particles into a total order. Since $C_i$ is discrete,
each particle will also need a tiebreaker variable $a_i$ to accompany it.
For iteration 1, $\{(C_i, a_i)\}_{i=1}^N$ will provide the total ordering.
We exclude the corner with the lowest corner count.

For iteration 2, we need a new quantity for total order (I think?), which
